Embedding Intuitionistic into Classical Logic

### 2022-07-09 CSL/lipics-v2021-EIICL.tex
modificaitons to abstract

\title{Embedding intuitionistic into classical logic} %TODO Please add

@@

%TODO mandatory: add short abstract of the document
\begin{abstract}
The famous double negation translation~\cite{glivenko1929quelques, godel1933intuitionistischen} establishes an embedding from classical into intuitionistic logic. Curiously the reverse direction has not been covered in literature. We present an effective embedding from intuitionistic to classical logic, both in the propositional and first-order case, as well as an effective embedding of intuitionistic propositional logic into quantified boolean formulas. 
Furthermore in the propositional case we establish a parameter that bounds the proof complexity of intuitionistic formulas. In this process we also present a Tseytin-like translation that preserves intuitionistic validity and reduces formulas to a normal form. The key notion used in the proofs is the existence of counter-models - an analogon to the satisfiability of the negation in classical logic, which is not equivalent to invalidity in the intuitionistic case.  We hope that this will allow leveraging the tremendous recent progress in automated reasoning in classical logic for checking intuitionistic validity, for which there has not been much progress in recent decades.
\end{abstract}

>>>>

\title{Embedding Intuitionistic into Classical Logic} %TODO Please add

@@

%TODO mandatory: add short abstract of the document
\begin{abstract}
The famous double negation translation~\cite{glivenko1929quelques, godel1933intuitionistischen} establishes an embedding from classical into intuitionistic logic. Curiously the reverse direction has not been covered in literature. We present an effective embedding from intuitionistic into classical logic, both in the propositional and first-order case, as well as an effective embedding of intuitionistic propositional logic into quantified boolean formulas.
Furthermore, in the propositional case we establish a parameter that bounds the proof complexity of intuitionistic formulas. As part of our construction, we also present a Tseytin-like translation that preserves intuitionistic validity and reduces formulas to a normal form.

%The key notion used in the proofs is the existence of counter-models - an analogon to the satisfiability of the negation in classical logic, which is not equivalent to invalidity in the intuitionistic case.  We hope that this will allow leveraging the tremendous recent progress in automated reasoning in classical logic for checking intuitionistic validity, for which there has not been much progress in recent decades.

We hope that our embeddings of classical into intuitionistic logic will allow leveraging the tremendous progress in automated reasoning in classical logic for checking intuitionistic validity, for which there has not been much progress in recent decades. Crucially, our constructions support the transfer of counter-models to validity, which is important to model checking applications, where the output of counter-examples is an appreciated feature.
\end{abstract}
